\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Updated the fig reference

```{r}
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 4.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15
#| out-height: 70%
#| fig-label: fig-rm-lg

>>>>

```{r}
#| label: fig-rm-lg
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal: (b) benchmark = 4.5$a_1$ and (c) benchmark = 2$a_1$, where $a_1$ = 0.09."
#| fig-height: 15
#| fig-width: 15
#| out-height: 70%

### 2024-10-07 paper.tex
Updated the fig reference

The decision on edge length removal is made based on the distribution of
edge lengths. In particular, a gap between values, where there a
concentration of small values and then a few larger values, likely
suggests a cutoff for edge removal. Because the triangulation is
typically done on the hexagon centroids, there are particular discrete
edge lengths, based on bin widths. \textbf{?@fig-rm-lg} illustrates edge
length distributions.

@@

{\centering \includegraphics[width=1\textwidth,height=0.7\textheight]{paper_files/figure-pdf/unnamed-chunk-36-1.pdf}

@@

\caption{Distribution of edge lengths and wireframes in \gD{} and
\(7\text{-}D\) with Delaunay triangulation, and two choices of long edge
removal: (b) benchmark = 4.5\(a_1\) and (c) benchmark = 2\(a_1\), where
\(a_1\) = 0.09.}

>>>>

The decision on edge length removal is made based on the distribution of
edge lengths. In particular, a gap between values, where there a
concentration of small values and then a few larger values, likely
suggests a cutoff for edge removal. Because the triangulation is
typically done on the hexagon centroids, there are particular discrete
edge lengths, based on bin widths. Figure~\ref{fig-rm-lg} illustrates
edge length distributions.

@@

\includegraphics[width=1\textwidth,height=0.7\textheight]{paper_files/figure-pdf/fig-rm-lg-1.pdf}

@@

\caption{\label{fig-rm-lg}Distribution of edge lengths and wireframes in
\gD{} and \(7\text{-}D\) with Delaunay triangulation, and two choices of
long edge removal: (b) benchmark = 4.5\(a_1\) and (c) benchmark =
2\(a_1\), where \(a_1\) = 0.09.}
